---
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{rmcqmcint Monte-Carlo and Quasi Monte-Carlo Integration}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8](inputenc)
---

Monte-Carlo and Quasi Monte-Carlo Integration
---------------------------------------------

Execute Monte-Carlo or Quasi Monte-Carlo Integration for given integrand
function.

There are two pre-defined Low discrepancy point sets,
Niederreiter-Xing point set and Sobol point set.
Both of them are selected to have low WAFOM.

Integrand function should recieve numeric vector and
shoud return numeic value.
Points passed to integrand are in the range (0, 1)^s.
Returned value of integration is mean of returned value of integrand,
not summation. To get summation, multiply by 2^m.


First, define an example integrand function; calculate n-sphere (0,1)^n.
```{r}
library(rmcqmcint)
unit.nsphere <- function(point) {
    if (sqrt(sum(point^2)) <= 1.0) {
        r <- 1.0
    } else {
        r <- 0.0
    }
    return(r)
}
```

example 1:
Calculate 4d-sphare by qmc, with default digital net.
```{r}
rs <- qmcint(integrand=unit.nsphere, N=100, s=4)
rs$mean
rs$absError
1 / 2 * pi^2 / 16 # to compare true value.
```

example 2:
Calculate 5d-sphare by qmc, with sobol sequence low WAFOM digital net.
```{r}
rs <- qmcint(integrand=unit.nsphere, N=100, s=5, digitalNetID = 2)
rs$mean
rs$absError
8 / 15 * pi^2 / 32 # to compare true value.
```

example 3:
Calculate 4d-sphare by mc.
```{r}
rs <- qmcint(integrand=unit.nsphere, N=100, s=4)
rs$mean
rs$absError
1 / 2 * pi^2 / 16 # to compare true value.
```

example 4:
Calculate 5d-sphare by mc.
```{r}
rs <- qmcint(integrand=unit.nsphere, N=100, s=5)
rs$mean
rs$absError
8 / 15 * pi^2 / 32 # to compare true value.
```
